---
title: "CFA Report"
author: "Aleksandr Blekh"
output:
  pdf_document:
    highlight: kate
    keep_tex: yes
    #lib_dir: figures/eda-report
    number_sections: yes
    toc: yes
    toc_depth: 3
    includes:
      in_header: ~/diss-floss/config/diss-floss.sty
  md_document:
    toc: yes
    toc_depth: 3
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    number_sections: yes
    theme: united
    toc: yes
  word_document:
    fig_width: 6.5
    mainfont: Calibri
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksEDA}
read_chunk('cfa.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareCFA}
# empty
```

```{r PerformCFA, cache=TRUE}
# empty
```

The SourceForge pilot data set consists of `r ncol(readRDS(file.path(READY4CFA_DIR, "flossData.rds")))` indicators. The following is the summary descriptive statistics of the data set.

```{r cfaReportSummary, include=TRUE, fig.cap='CFA Report'}
print(summary(cfaFit_flossData, fit.measures = TRUE, standardize = TRUE))
```

And now let's see what output would be produced by 'xtable' package:

```{r cfaReportSummary2, include=TRUE, results='asis', fig.cap='CFA Results Summary'}
#print(xtable(cfaTable_flossData, caption="CFA Results Summary",
#             digits = 2),
#      comment = FALSE,
#      include.rownames = FALSE)
```

And now let's see what output would be produced by 'tables' package:

```{r cfaReportSummary3, include=TRUE, results='asis', fig.cap='CFA Results Summary'}
print(genCFAresultsTable())
```

And let's generate a nice CFA model figure:

```{r cfaModelFigure, include=TRUE, fig.cap='CFA Model', fig.height=4, fig.width=4}
# DO NOT ADD fig.align='center' option before the issue #626 is not fixed (tentative fix revision: knitr 1.8)
#print("", quote = FALSE)
#print(screePlot_flossData)
```
