---
title: "CFA Report"
author: "Aleksandr Blekh"
output:
  pdf_document:
    highlight: kate
    includes:
      in_header: ~/diss-floss/config/diss-floss.sty
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  md_document:
    toc: yes
    toc_depth: 3
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    number_sections: yes
    theme: united
    toc: yes
  word_document:
    fig_width: 6.5
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksEDA}
read_chunk('cfa.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
outFmt <- opts_knit$get('out.format')
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareCFA}
# empty
```

```{r PerformCFA, cache=TRUE}
# empty
```

The SourceForge pilot data set consists of `r ncol(readRDS(file.path(READY4CFA_DIR, "flossData.rds")))` indicators. The following is the summary descriptive statistics of the data set.

```{r cfaReportSummary, include=TRUE, background='grey90', output.lines=1:120}
summary(cfaFit_flossData, fit.measures = TRUE, standardize = TRUE)
```

Let's see how equations work:

$$ \sum_{i=1}^{n} \{ y_{i} - \hat{\mu}_{i} \}^2 $$

Another one:

$$ \sum_{i=1}^{n} \{ y_{i} - \hat{\mu}_{i} \}^2 $$

And now let's see what output would be produced by 'tables' package, as shown in Table \ref{cfaResultsTable}:

```{r cfaReportSummary3, include=TRUE, results='asis', fig.cap='CFA Results Summary'}
#if (outFmt == 'word_document') fileType <- 'msword'
#genCFAresultsTable(label = "cfaResultsTable", type = fileType)
genCFAresultsTable(label = "cfaResultsTable")
```

Results of CFA in a form of a model diagram are presented in Figure \ref{fig:cfaModelDiagram}:

```{r cfaModelFigure, include=FALSE, results='asis', fig.cap='CFA Model', fig.height=4, fig.width=4}
# DO NOT ADD fig.align='center' option before the issue #626 is not fixed (tentative fix revision: knitr 1.8)
genCFAmodelDiagram(cfaFit_flossData, latex = TRUE, caption = "CFA model diagram", label = "cfaModelDiagram")
```

\begin{figure}
  \centering
  % \scalebox{1.0}[1.25]{\input{cfaModDiag.tex}}
  \input{cfaModDiag.tex}
  \caption{CFA model diagram}
  \label{fig:cfaModelDiagram}
\end{figure}
