---
title: "EDA Report"
author: "Aleksandr Blekh"
output: html_document
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r SetOptions, echo=F, message=F}
require(knitr)
# getwd()
opts_chunk$set(
  results='show',
  message = TRUE,
  comment = NA,
  tidy = FALSE,
  fig.width = 8.5,
  fig.height = 11,
  out.width = NULL,
  fig.path = 'figures',
  dev = "svg",
  dpi = 400
)
echoChunks <- FALSE
warningChunks<- FALSE
options(width=120)  # so the output is 50% wider than the default
read_chunk("eda.R") # the file to which knitr calls for the chunks
```

```{r Prepare, echo=F, message=FALSE, results='hide'}
# load packages etc.
```

```{r FullEDA, echo=echoChunks, message=F}
```
