---
title: "EDA Report"
author: "Aleksandr Blekh"
output:
  pdf_document:
    fig_caption: no
    fig_crop: no
    fig_width: 8
    highlight: kate
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  md_document:
    toc: yes
    toc_depth: 3
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    fig_width: 8
    number_sections: yes
    theme: united
    toc: yes
  word_document:
    fig_width: 6.5
    mainfont: Calibri
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksEDA}
read_chunk('eda-knitr.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareEDA}
# empty
```

```{r CustomFunctions}
# empty
```

```{r PerformEDA, echo=TRUE}
# empty
```
