---
title: "EFA Report"
author: "Aleksandr Blekh"
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    highlight: kate
    includes:
      in_header: ~/diss-floss/config/diss-floss.sty
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  md_document:
    toc: yes
    toc_depth: 3
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    number_sections: yes
    theme: united
    toc: yes
  word_document:
    fig_width: 6.5
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksEDA}
read_chunk('efa.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareEFA}
# empty
```

```{r PerformEFA, cache=TRUE}
# empty
```

```{r getRefInfo}
#bcRefInfo <- genObjRefs("fig", "barchart_")
#histRefInfo <- genObjRefs("fig", "histogram_")
#mixpRefInfo <- genObjRefs("fig", "mixplot_")
#pmatRefInfo <- genObjRefs("fig", "plotmatrix_")
```

The SourceForge pilot data set consists of `r ncol(readRDS(file.path(READY4EFA_DIR, "flossData.rds")))` indicators. The following is the summary descriptive statistics of the data set.

```{r efaReportVssSummary, include=TRUE, results='markup'}
summary(vssInfo_flossData)
```

And now let's take a look at the EFA results summary, presented in Table \ref{tab:efaResults}:

```{r efaReportSummaryTable, include=TRUE, results='asis'}
genEFAresultsTable(caption="EFA Results: Summary by rotation method", digits=2, numFactors=numFactors)
```

The factors scree plot, produced as part of EFA, is shown in Figure \ref{fig:efaResultsScreePlot}:

```{r efaReportScreePlot, include=TRUE, fig.cap='EFA Results: Scree plot\\label{fig:efaResultsScreePlot}'}
# DO NOT ADD fig.align='center' option before the issue #626 is not fixed (tentative fix revision: knitr 1.8) -- TODO: update when 1.8 will be released
print(screePlot_flossData)
```

Results of EFA are visualized in a form of diagrams and are presented in Figure \ref{fig:efaResultsDiagram} below:

`r diagLegend <- "DTS - Development Team Size; PrA - Project Age; LcR - License Restrictiveness; PrS - Project Size; SfT - Software Type"`

```{r efaReportDiagram, include=TRUE, results='asis', fig.cap='EFA Results: Model diagram\\label{fig:efaResultsDiagram}', fig.show='hold'}
genEFAresultsDiagram(efaModels, TRUE, latex = TRUE)
```

```{r efaResultsDiagramAppendix, include=FALSE, results='asis', fig.cap='EFA Results Diagrams (continued)', fig.show='hold', fig.height=3.5, fig.width=3.5}
if (DO_APPENDIX)
genEFAresultsDiagram(efaModels, latex = TRUE)
```
