---
title: "EFA Report"
author: "Aleksandr Blekh"
output:
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    number_sections: yes
    theme: united
    toc: yes
  md_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    highlight: kate
    keep_tex: yes
    lib_dir: figures/eda-report
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    fig_width: 6.5
    mainfont: Calibri
---

The following report is dynamically generated and presents results of exploratory data analysis (EDA) for prepared (transformed) research data, located in directories under "data/transform".

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksEDA}
read_chunk('efa.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareEFA}
# empty
```

```{r PerformEFA, cache=TRUE}
# empty
```

The SourceForge pilot data set consists of `r length(dir(file.path(TRANSFORM_DIR, "SourceForge")))` indicators. The following is the summary descriptive statistics of the data set.

```{r efaReportSummary, include=TRUE, fig.cap='EFA Report'}
print(summary(vssInfo_var))
```

And now let's see what output would be produced by 'xtable' package:

```{r efaReportSummary2, include=TRUE, results='asis', fig.cap='EDA Report'}
#print(xtable(describe_flossData, caption="flossData Summary",
#             digits=3),
#      comment = FALSE,
#      include.rownames = FALSE)
genEFAresultsTable(caption="EFA results summary", digits = 2)
```
