---
title: "SEM Report"
author: "Aleksandr Blekh"
output:
  pdf_document:
    fig_caption: yes
    highlight: kate
    includes:
      in_header: ~/diss-floss/config/diss-floss.sty
    keep_tex: yes
    number_sections: no
    toc: no
    toc_depth: 3
  md_document:
    toc: yes
    toc_depth: 3
  html_document:
    css: ~/diss-floss/config/knitr/markdown.css
    number_sections: yes
    theme: united
    toc: yes
  word_document:
    fig_width: 6.5
---

Following standard research methodology approach, prior to the core phases of data analysis (CFA and SEM, for this study), an exploratory data analysis (EDA) was performed. Please note, that exploratory factor analysis (EFA), while also exploratory in nature, corresponds to further phase of this study and, thus, the corresponding section is located outside of the current one. Since both pilot and main data sets are identical parts of the same randomly selected data set and all further statistical analysis had to be performed, using either of the two, the EDA was performed, using only the pilot data set.

This EDA consists of performing both descriptive and visual exploratory analysis for single variables (univariate), as well as for relationships between variables (multivariate).

```{r KnitrSetup, child='../config/knitr/knitr-setup-global.Rmd'}
# empty
```

```{r ReadChunksSEM}
read_chunk('sem.R')
```

```{r CleanEnv}
# empty
```

```{r ConfigReport}
param1 <- TRUE
param2 <- FALSE
param3 <- 'TEST'
```

```{r LoadPackages}
# empty
```

```{r PrepareSEM}
# empty
```

```{r CustomFunctions}
# empty
```

```{r PerformSEM, cache=TRUE}
# empty
```

### SEM Resuls

Descriptive statistics. The SourceForge pilot data set consists of `r length(dir(file.path(TRANSFORMED_DIR, "SourceForge")))` indicators. The descriptive statistics of the pilot data set, including measures of central tendency (_mean, median_), position (_minimum, maximum, quantiles_), dispersion (_variance, standard deviation, range and interquartile range_) and shape (_modality, skewness and kurtosis_), is summarized in Table \ref{tab:semResultsTable1} below.

```{r semReportSummary, include=TRUE, render=pander, results='asis'}
genSEMtable(summary(successPLS), type = "1", caption = "SEM results summary", label = "semResultsTable1")
```

A visual presentation of SEM results includes various types of graphical output. In particular, factor loadings are visually presented in Figure \ref{fig:semLoadingsDiagram}. Discussion continues.

`r loadDiag <- genSEMfigure(plspm_flossData, caption = "SEM: Loadings diagram", label = "semLoadingsDiagram")`

```{r semLoadingsDiag, include=TRUE, results='asis', fig.cap=loadDiag$caption}
plot(plspm_flossData, what = "loadings")
```

`r lowLoadingsIndicators <- "License.Restrictiveness and Project.Stage"`

Barchart of loadings, shown in Figure \ref{fig:semLoadingsBarChart}, presents information in relation to the threshold value (`r LOADINGS_THRESHOLD`) and grouped by latent factors (blocks). As we see, loadings for _`r lowLoadingsIndicators`_ are insufficient for this data set and original SEM model.

`r loadBarChart <- genSEMfigure(gLoadBarChart, caption = "SEM: Barchart of loadings", label = "semLoadingsBarChart")`

```{r semLoadingsBChart, include=TRUE, results='asis', fig.cap=loadBarChart$caption}
print(loadBarChart$plot)
```

A diagram with estimated factor weights is presented in Figure \ref{fig:semWeightsDiagram}. Discussion continues.

`r weightsDiag <- genSEMfigure(gLoadDiag, caption = "SEM: Weights diagram", label = "semWeightsDiagram")`

```{r semWeightsDiag, include=TRUE, results='asis', fig.cap=weightsDiag$caption}
plot(plspm_flossData, what = "weights")
```

Chart, shown in Figure \ref{fig:semCrossLoadBlocks}, presents cross-loadings between indicators, grouped by latent factors (blocks). As we see, TBD.

`r crossLoadBlocks <- genSEMfigure(gCrossLoadBlocks, caption = "SEM: Barchart of cross-loadings by factors", label = "semCrossLoadBlocks")`

```{r semCrossLoadBlocksChart, include=TRUE, results='asis', fig.cap=crossLoadBlocks$caption}
print(crossLoadBlocks$plot)
```

TODO: More narrative and more visual artifacts.
